EEG characterization and classification based on histograms of image gradients

### 2016-12-22 article.tex
Added explanation of P300 phenomena and some minor typos

The proposed algorithm was developed to perform a binary classification task, determining the appearance on each corresponding signal segment of the P300 response.  If it was present, the segment was labelled as class 1, a \textit{hit}, and its absent was identified as class 2, a \textit{no-hit}.

>>>>

The proposed algorithm was developed to perform a binary classification task, determining the appearance or not of the P300 response on each corresponding signal segment.  If it was present, the segment was labelled as class 1, a \textit{hit}, and its absent was identified as class 2, a \textit{no-hit}.
